00_census_data

### 2024-11-05 data-raw/00_census_data.qmd
Added a relevant variable that was missing from the census data tables, and updated the documentation

```{r}
# save(
#   census_data_da, 
#   , 
#   region_backgrounds, 
#   file = "./data/census_data.Rdata")
```

@@

for(i in regions){
  census_data_cma |>
    rename(region = r5r_analysis_region) |>
    filter(region == i) |>
    select(Type, GeoUID, name, region) |>
    assign(x = glue::glue("census_data_cma_{i}"),
         value = _)

@@

Save DA data by region:
```{r}
for(i in regions){
  census_data_da |>
    rename(region = r5r_analysis_region) |>
    filter(region == i) |>
    select(-c(`Shape Area`, `Region Name`, `Area (sq km)`, popn_dens, `study_region_name`)) |>
    select(Type, GeoUID, region, everything()) |>
    assign(x = glue::glue("census_data_da_{i}"),
         value = _)

>>>>

@@

for(i in regions){
  census_data_cma |>
    rename(region = r5r_analysis_region) |>
    filter(region == i) |>
    select(Type, GeoUID, name, region, study_region_name) |>
    assign(x = glue::glue("census_data_cma_{i}"),
         value = _)

@@

Save DA data by region:
```{r}
for(i in regions){
  census_data_da |>
    rename(region = r5r_analysis_region) |>
    filter(region == i) |>
    select(-c(`Shape Area`, `Region Name`, `Area (sq km)`, popn_dens)) |>
    select(Type, GeoUID, region, everything()) |>
    assign(x = glue::glue("census_data_da_{i}"),
         value = _)
